Graph Topology Learning from Binary Signals on Graph

### 2022-04-28 poster html copy/poster html.Rmd
Updated logos.

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: Chico-State-Flame-Cardinal300dpi.png
# logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

@@

```{r GTG, echo=FALSE,out.width="90%", out.height="25%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2. Each edge weight follows uniform random distribution on (0,1). Grey nodes indicate a signal value of 0 and black nodes indicate a signal value of 1.",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/gt_graph.png"))
```

@@

```{r EAG, echo=FALSE,out.width="60%", out.height="10%",fig.cap="Circular Embedding of Estimated graph. Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/est_graph.png"))
``` 
# Discussion
To our knowledge, this is the first work on learning graph topology from binary signals. We have developed a method to effectively learn the graph adjacency matrix from binary signals. This model can be easily extended for learning binomial signals in general. Incorporating parameter optimization techniques would be a natural improvement on this model. Moreover, it would be desirable to develop scalable algorithms that can be used to learn a topology for a large graph from signals. Recently, in @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn improving the over-all runtime.

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```
# Acknowledgement
This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work for Data Science Capstone Project.

>>>>

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: pictures/DSI_Hexbin_sticker_01.png
#logoright_name: pictures/logo1.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

@@

```{r GTG, echo=FALSE,out.width="80%", out.height="25%",fig.cap="Circular Embedding of random Erd&#337;s-Reyni Graph with edge probability p = 0.2. Each edge weight follows uniform random distribution on (0,1). Grey nodes indicate a signal value of 0 and black nodes indicate a signal value of 1.",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/gt_graph.png"))
```

@@

```{r EAG, echo=FALSE,out.width="80%", out.height="25%",fig.cap="Circular Embedding of Estimated graph. Note the overall weight of each edge is smaller than the edge weights of the ground truth.",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/est_graph.png"))
``` 
# Discussion
To our knowledge, this is the first work on learning graph topology from binary signals. We have developed a method to effectively learn the graph adjacency matrix from binary signals. This model can be easily extended for learning binomial signals in general. Incorporating parameter optimization techniques would be a natural improvement on this model. Moreover, it would be desirable to develop scalable algorithms that can be used to learn a topology for a large graph from signals. Recently, in @saboksayr2021accelerated the author shows fast proximal-gradient iterations can be applied to the framework given by @kalofolias2016learn improving the over-all runtime.

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```
# Acknowledgement

 <body>      
        <p style="color:black;font-size:24px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>    
</body>

```{r , echo=FALSE,out.width="60%", out.height="10%",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/logo1.png"))
```
